\LARGE TN1008 \\ Advanced Simulation and Visualization of Fluids in Computer Graphics \\ \Large Divergence-Free Smoothed Particle Hydrodynamics

### 2016-12-05 report/paper.tex
started introduction and writing on cell list

\firstsection{Introduction}
\maketitle 
%explain the context of the work:
	%What exactly is the problem?
	%What have you created?

\section{Background and Related Work}
%What have people done before?
	%When addressing this problem, when addressing similar problems
%What have you done that makes you approach different?
Based on~\cite{bender}

\section{Method}
%What have you done?
%How did you do it?
%Why did you do it that way?
%May want to mention why you *didn’t* do it in some 
%other possible way
%Clear enough that you could hand the report to another student and they could reproduce the work!
%Probably no need to mention programming language etc
\subsection{Neighbourhood search}
\subsection{Divergence solver}
\subsection{Density solver}
\subsection{Kernel}
\subsection{Navier-stokes}
% Write about non pressure forces, velocity osv..?
\subsection{Adapted time step}
\subsection{Density and alpha factors}

@@

\bibliographystyle{abbrv}
\bibliography{./refs}

>>>>

\firstsection{Introduction}
\maketitle 
    %explain the context of the work:
	%What exactly is the problem?
	%What have you created?
    Smoothed particle hydrodynamics, \textit{SPH}, is a method that was first implemented in 1977 for astrophysical simulations by Gingold et al.~\cite{firstSPH}.
    Since then SPH has become a popular method for complex water simulations.
    SPH is a mesh-free Lagrangian method where the particles move in space and change physical properties as time progresses.
    % More about Lagrangian and maybe navier stokes?

    % We used this article
    In this paper we are going to introduce the results from reproducing the divergence-free smoothed particle hydrodynamics method introduced by Bender et al.~\cite{bender}.
    It is a method which corrects the divergence error, aiming for a divergence-free velocity field which is needed for an incompressible fluid.
    For the solution to be divergence-free the density has to be constant over time.

    % Write about other solutions? Why is this solution the BEST!!?

\section{Background and Related Work}
    %What have people done before?
	%When addressing this problem, when addressing similar problems
    %What have you done that makes you approach different?

    % Bridson
    ~\cite{bridson}.

    % Write about Benders article

\section{Method}
%What have you done?
%How did you do it?
%Why did you do it that way?
%May want to mention why you *didn’t* do it in some 
%other possible way
%Clear enough that you could hand the report to another student and they could reproduce the work!
%Probably no need to mention programming language etc
\subsection{Neighbourhood search}
    Since SPH only considers a finite amount of neighbouring particles, it is important to keep track of every particles neighbours.
    Searching through all particles for neighbours within the cutoff distance $H$ for every particle is inefficient and takes $\mathcal{O}({N^2})$ time.
    The cutoff distance $H$ is the kernel smoothing radius.
    To fasten this up a cell list was implemented.
    A cell list is a data structure that is divided into cells that have a length larger or equals to the cutoff distance $H$.
    When finding the neighbour of particle $i$, only the neighbouring cells have to be searched for particles within the cutoff distance, see figure~\ref{fig:cellList}.

    \begin{figure}
    \includegraphics[width=\linewidth]{img/CellLists2.png}
    \caption{Finding the neighbours for the filled in particle $i$ by looking through all neighbouring cells, including its own cell, for particles within the cutoff distance $H$}
    \label{fig:cellList}
    \end{figure}

    The cell list is implemented by using a four dimensional vector where the first three dimensions are for the x, y and z coordinates for the cells and the fourth dimension is for storing the particles belonging to the cell.
    The amount of cells are decided by dividing the scene into cells of length $H$.
    The particles are then assigned to a cell.
    If the particle moves out of its cell it is then assigned to the new cell.

    \begin{equation} \label{eq:assignCell}

    \end{equation}

\subsection{Divergence solver}
\subsection{Density solver}
\subsection{Kernel}
\subsection{Navier-stokes}
% Write about non pressure forces, velocity osv..?
\subsection{Adapted time step}
\subsection{Density and alpha factors}
\subsection{Screen space fluid rendering}

@@

%\bibliographystyle{abbrv}
\bibliographystyle{ieeetr}
\bibliography{./refs}
